A perfect storm and the natural endowments of trade-enabling infrastructure

### 2023-06-07 Slides/20min/20min.Rmd
Update slides

.pull-left[
- Danish Demographic Database 
- Individual-level data for the years 1787, 1801, 1834, 1845, 1860, 1870, 1890 and 1901 
- From this: Parish level population counts + occupations 
- New procedure to automatically make [HISCO labels](#hisco)

@@

---
.pull-left[
### Part 1
<p style="color:red;">The channel caused fishing and manufacturing:</p>

**Fishing:**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/fish.png")
```

]
--
.pull-right[
### Part 2
<p style="color:red;">But only manufacturing can account for the population growth:</p>

**Manufacturing:**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/manu.png")
```

@@

**Data?** 
- Just use register data! 
- New method to construct panel sampling $P(Coin|t)_i$ from dating range based on Bayes and Monte Carlo
]

>>>>

.pull-left[
- Link Lives 
- Individual-level data for the years 1787, 1801, 1834, 1845, 1860, 1870, 1890 and 1901 
- From this: Parish level population counts + occupations 
- New procedure to automatically make [HISCO labels](#hisco)

@@

---
.pull-left[
**Fishing:**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/fish.png")
```

]
--
.pull-right[
**Manufacturing:**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/manu.png")
```

@@

**Data?** 
- Just use register data! 
- Turning dating range + coordinate into panel of economic activity
]
